The impact of cosmic variance on simulating weak lensing surveys

### 2014-11-11 Writeup/paper_v3.tex
avoid annoying CFHTLenS people with completely true statement that they do not like to hear

The intrinsic ellipticity distribution plays a role in nearly all
shear estimators.  In some, the role is explicit: for example, LensFit
\citep{2007MNRAS.382..315M,2008MNRAS.390..149K,2013MNRAS.429.2858M}
and the methods presented by \cite{2014MNRAS.438.1880B} require
accurate intrinsic ellipticity distributions as inputs, and
uncertainty in the distribution was one of the important sources of
systematic uncertainty in the CFHTLenS weak lensing results
\citep{2013MNRAS.432.2433H,2013MNRAS.429.2858M}.  In others, the role
is implicit.  For example, the re-Gaussianization method and several
other moment-based methods require calculation of a shear responsivity
\citep{BJ02,HS03} that describes how the galaxy population overall
responds to a shear, based on its intrinsic ellipticity distribution.
The responsivity can be calculated based on the observed shape
distribution, assuming that the uncertainties in the shears are known
enough that their contribution to that distribution can be removed.
If a simulated sample in some redshift slice has a different intrinsic
ellipticity distribution and therefore responsivity, it could lead to
incorrect conclusions about shear calibration.  The responsivity
scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
RMS ellipticity at the level of 0.01 (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased}) would become fractional shear
errors of
\begin{equation}
\frac{\Delta\gamma}{\gamma} \approx \frac{2 e_\text{RMS} \Delta
  e_\text{RMS} }{1-e_\text{RMS}^2} \approx 0.01.
\end{equation}
In the context of upcoming lensing surveys that seek to constrain
shears to the per cent level or better, a systematic error of this
magnitude in shear calibration is quite serious.

>>>>

The intrinsic ellipticity distribution plays a role in nearly all
shear estimators.  In some, the role is explicit: for example, LensFit
\citep{2007MNRAS.382..315M,2008MNRAS.390..149K,2013MNRAS.429.2858M}
and the methods presented by \cite{2014MNRAS.438.1880B} require
accurate intrinsic ellipticity distributions as inputs, and
uncertainty in the distribution was one source of
systematic uncertainty in the CFHTLenS weak lensing results
\citep{2013MNRAS.432.2433H,2013MNRAS.429.2858M}.  In others, the role
is implicit.  For example, the re-Gaussianization method and several
other moment-based methods require calculation of a shear responsivity
\citep{BJ02,HS03} that describes how the galaxy population overall
responds to a shear, based on its intrinsic ellipticity distribution.
The responsivity can be calculated based on the observed shape
distribution, assuming that the uncertainties in the shears are known
enough that their contribution to that distribution can be removed.
If a simulated sample in some redshift slice has a different intrinsic
ellipticity distribution and therefore responsivity, it could lead to
incorrect conclusions about shear calibration.  The responsivity
scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
RMS ellipticity at the level of 0.01 (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased}) would become fractional shear
errors of
\begin{equation}
\frac{\Delta\gamma}{\gamma} \approx \frac{2 e_\text{RMS} \Delta
  e_\text{RMS} }{1-e_\text{RMS}^2} \approx 0.01.
\end{equation}
In the context of upcoming lensing surveys that seek to constrain
shears to the per cent level or better, a systematic error of this
magnitude in shear calibration is quite serious.
